### 2019-09-22 paper/3_3_generalizing_the_dantzig_selector_bound.tex
Use BibTeX, conform to IEEE citation style

The third and last part of our task is to plug in the almost-sparsity found in Section 3.1, and plug in the probablity found in Section 3.2.
Set for short
\PF {d:g,g}
\Disp {
\NC \V {d} 
= \NC \Hat {\V {g}} -\V {g} \NR
}
And our task is to bound its expectation.

We argue that \m {\V{g}} can essentially be seen as sparse, and for that purpose we ignore relevent terms.
Also, we do not seek a very tight bound and will approximate \m {\d_{S}} by \m {1}.
And, as shall be seen, it suffices to set
\Disp {
\NC \g 
= \NC \R {2 \log N_h} \NR
}

The rest follows \quotation {The Dantzig Selector} very closely.
The generalization to complex vector is necessary in our setting.
We spell out the proof when such generalization is nontrivial.

\Result
{Lemma}
{
Let \m {\V {g}} and \m {\V {d}} be defined as above.
Then
\Disp {
\NC \VNm {\V {d} _{\MC {K}}} _1
\leq \NC \VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {K}}} _1 \NR
}
}

To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {K}},
\Disp {
\NC \VNm {\V {g}} _1
-\VNm {\V {d} _{\MC {A}}} _1
+\VNm {\V {d} _{\MC {K}}} _1
-\VNm {\V {g} _{\MC {K}}} _1
\leq \NC \VNm {\V {g} +\V {d}} _1 \NR
}
In the first line, we recall \m {\V {g} =\V {g} _{\MC {A}}}.
On the other hand, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
\Disp {
\NC \VNm {\V {g} +\V {d}} _1
=\NC \VNm {\hat {\V {g}}} _1 \NR
\NC \leq \NC \VNm {\V {g}} _1 \NR
}
The result follows by combining.

\Result
{Lemma}
{
\Disp {
\NC \MB {E} \SB {\Nm {\IP {\V {z} \SB {\o_z}, \M {P} \DB {:, n_h}}}}
\leq \NC  2 \R {\log N_h} \NR
\NC n_h 
=\NC 1, \ldots, N_h. \NR
}
with probability \m {\geq 1 -N_h^{-1}}.
}

Indeed, recall the fact that \m {\M {P} \DB {:, n_g}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}.

Recall the following bound for \m {Q} function
\Disp {
\NC Q\SB {x}
\leq \NC \F {1}{2} \Ss {e}^{-x^2/2} \NR
}
Particularly, for \m {x =\R {2 \log N_h}},
\Disp {
\NC Q\SB {\R {2 \log N_h}}
=\NC \F {1}{N_h}. \NR
}

\Result
{Lemma}
{
With the condition that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M{P}}},
\Disp {
\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
\leq \NC  4 \R {\log N_h} \NR
}
with probability \m {\geq 1 -N_h^{-1}}.
}

To show this, by definition
\Disp {
\NC \IP {\V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y}}
= \NC \IP {\M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} \DB {:,n_y}} \NR
\NC = \NC \IP {\M {P} \V {d}, \M {P} \DB {:,n_y}} \NR
}
By construction
\Disp {
\NC \VNm {\M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty
\leq \NC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty \NR
\NC \leq \NC 2\R {\log N_h} \NR
}
By triangle inequality, together with Lemma (), we have
\Disp {
\NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} _\infty
\leq \NC \VNm {\IP {\V {z}, \M {P} \DB {:,n_y}}} _\infty
+\IP {\V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y}} \NR
\NC \leq \NC 2 \R {\log N_h} +2 \R {\log N_h} \NR
}
which implies
\Disp {
\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
\leq \NC 4 \R {\log N_h}. \NR
}

From \quotation {Dantzig Selector} Lemma 1, first equation, we have the result as below.
The original result is for real vector spaces, but we have checked that the proof is completely valid in complex vector spaces.
The only thing that has to change accordingly is the interpretation of magnitude and the inner product, which are evident.

\Result
{Lemma}
{
With the condition that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M{P}}},
\Disp {
\NC \VNm {\V {d} _{\MC {AB}}} _2
\leq \NC \F {1}{1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3S}}{\RB {1-\d_{2S}} \R {S}} \VNm {d_{\MC {K}}} _1 \NR
}
}

From \quotation {Dantzig Selector}, Lemma 1, second equation, we have the result as below.
Again, their proof works with complex vector spaces in place of real ones too.

\Result
{Lemma}
{
\Disp {
\NC \VNm {\V {d}} _2^2
\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1}{S} \VNm {\V {d} _{\MC {K}}} _1^2 \NR
}
}

@@

We are going to combine previous lemmata and show the main result.

In accordance with (), set
\Disp {
\NC S
=\NC s^2 L \NR
}
If we set again \m {s =\R{N_H}}, we get \m {S =N_H L}.

\Result
{Theorem}
{
Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
Then the bound
\Disp {
\NC \VNm {\V {d}} _2
\leq \NC 4 \R{2} \D \R{L N_H \log N_H} \NR
}
holds for probability \m {p}, with
\Disp {
\NC 1 -p
\leq \NC 2 \D 6^S \D \exp \SB {-\F{N_Y^2} {32}} \NR
}
}

The first quantity we want to bound away is
\Disp {
\NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
\leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
\NC \leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
\NC \leq \NC 4 \R {S \log N_h} \NR
}
Thus, by virtue of Lemma (), and approximating \m {1 /(1 -\d_{2S}) =1 +\d_{2S}} and so on,
\Disp {
\NC \VNm {\V {d}_{\MC {A}}} _1
\leq \NC \R {S} \VNm {\V {d}_{\MC {A}}} _2 \NR
\NC \leq \NC \R {S} \VNm {\V {d} _{\MC {AB}}} _2 \NR
\NC \leq \NC \d_{3S} \RB {1+\d_{2S}} \VNm {\V {d} _{\MC {K}}} _1
+4 \RB {1+\d_{2S}} S \R {\log N_h} \NR
}

Next, we must eliminate \m {\VNm {d _{\MC {A}}} _1} in rhs of Lemma ().
\Disp {
\NC \VNm {\V {d} _{\MC {K}}} _1
\NC \leq \d_{3S} \RB {1+\d_{2S}} \VNm {\V {d} _{\MC {K}}} _1
+4 \RB {1+\d_{2S}} S \R {\log N_h}
+2 \VNm {\V {g} _{\MC {K}}} _1 \NR
}
Arranging and drop second order small terms like \m {\d_{2S} \d_{3S}}, that is,
\Disp {
\NC 1 \ll \NC S \NR
\NC \ll \NC N_h \NR
}
doing this we have
\Disp {
\NC \VNm {\V {d} _{\MC {K}}} _1
\leq \NC 2 \RB {1+\d_{3S}} \VNm {\V {g} _{\MC {K}}} _1
+4 \RB {1+2\d_{3S}} S \R {\log N_h} \NR
}

We are now in a position to bound \m {\VNm {d} _2^2}.
Using Lemma () again, and only keeping to first order, we have
\Disp {
\NC \VNm {\V {d}} _2^2
\leq \NC 16 S \log N_h
+8 \d_{3S} \R {\log N_h} 
+\F {\d_{3S}^2} {S} \VNm {\V {d} _{\MC {K}}} _1 \NR
}
Finally, plug in the bound for \m {\VNm {\V {d} _{\MC {K}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d} _{\MC {K}}} _1}.
Again for simplicity, we keep only the first order small terms.
Plug in \m {S =s^2 L} and \m {N_h =N_H^2} we get, finally,
\Disp {
\NC \VNm {\V {d}} _2^2
\leq \NC 32 S \log N_H
+\F {8 \R {2\pi}} {3} \d_{3S} L \R {\F {\log N_H} {N_H}}
+\F {\pi} {9} \F {L} {s^2 N_H} \NR
}
Set \m {\d_S =1} for the worst situation, and we get the desired bound.

>>>>

The third and last part of our task is to plug in the almost-sparsity found in Section 3.1, and plug in the probablity found in Section 3.2.
Set for short
\PF {d;g,g}
\DispN {
\NC \V {d} 
= \NC \Hat {\V {g}} -\V {g} \NR
}
And our task is to bound the expectation \m {\MB {E} \SB {\V {d}}}.

We argue that \m {\V {g}} can essentially be seen as sparse, and for that purpose we ignore relevent terms.
Also, we do not seek a very tight bound and will approximate \m {\d_{S}} by \m {1}.
And, as shall be seen, it suffices to set
\PF {g';2,nn-h}
\DispN {
\NC \g
= \NC \R {2 \log N_h} \NR
}

The rest follows \quotation {The Dantzig Selector} very closely, but sometimes, the generalization to complex vector cannot be glossed over, and we have to examine.
To start, we state several lemmata (or their generalization) shown in their paper.

\Result
{Lemma}
{
\PF {d-K;d-A,2-g-K}
\DispN {
\NC \VNm {\V {d} _{\MC {C}}} _1
\leq \NC \VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {C}}} _1 \NR
}
}

To show this, observe that with triangle inequality applied respectively on \m {\MC {A}} and \m {\MC {C}}, while recalling that \m {\V {g} =\V {g} _{\MC {A}}},
\PF {g,d-A,d-K}
\DispN {
\NC \VNm {\V {g}} _1
-\VNm {\V {d} _{\MC {A}}} _1
+\VNm {\V {d} _{\MC {C}}} _1
-\VNm {\V {g} _{\MC {C}}} _1
\leq \NC \VNm {\V {g} +\V {d}} _1 \NR
\NC =\NC \VNm {\hat {\V {g}}} _1 \NR
}
On the other hand, by construction that \m {\hat {g}} minimizes the \m {\ell_1}-norm,
\PF {g,d;g}
\DispN {
\NC \leq \NC \VNm {\V {g}} _1 \NR
}

\Result
{Lemma}
{
Let \m {\M {P}} be fixed, and instance of \m {\V {z}} be given.
Then the relation
\PF {E,z,P}
\DispN {
\NC \MB {E} \SB {\Nm {\IP {\V {z} , \M {P} \DB {:, n_h}}}}
\leq \NC  2 \R {\log N_h} \NR
\NC n_h 
=\NC 1, \ldots, N_h. \NR
}
holds with probability \m {\geq 1 -N_h^{-1}}.
}

Indeed, recall the fact that \m {\M {P} \DB {:, n_g}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}, the quantity \m {\Nm {\IP {\V {z} , \M {P} \DB {:, n_h}}}} observes standard Normal.
Recall the following bound for \m {Q} function
\PF {Q,x;1}
\DispN {
\NC Q\SB {x}
\leq \NC \F {1} {2} \Ss {e}^{-x^2/2} \NR
}
Particularly, for \m {x =\R {2 \log N_h}},
\PF {Q,2;nn-h}
\DispN {
\NC Q\SB {\R {2 \log N_h}}
=\NC \F {1} {N_h}. \NR
}

\Result
{Lemma}
{
With the assumption that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M {P}}}, then
\PF {P,P,d}
\DispN {
\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
\leq \NC  4 \R {\log N_h} \NR
}
holds with probability \m {\geq 1 -N_h^{-1}}.
}

To show this, by definition
\PF {z,y,P}
\DispN {
\NC \IP {\V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y}}
= \NC \IP {\M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} \DB {:,n_y}} \NR
\NC = \NC \IP {\M {P} \V {d}, \M {P} \DB {:,n_y}} \NR
}
By construction
\PF {P,n-y,y}
\DispN {
\NC \VNm {\M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty
\leq \NC \VNm {\M {P}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty \NR
\NC \leq \NC 2\R {\log N_h} \NR
}
By triangle inequality, together with Lemma (), we have
\PF {P,n-y,y}
\DispN {
\NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} _\infty
\leq \NC \VNm {\IP {\V {z}, \M {P} \DB {:,n_y}}} _\infty
+\IP {\V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y}} \NR
\NC \leq \NC 2 \R {\log N_h} +2 \R {\log N_h} \NR
}
which implies
\PF {P,P,d} \DispN {
\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
\leq \NC 4 \R {\log N_h}. \NR
}

The following two lemmata, coming from \quotation {Dantzig Selector} Lemma 1, will be stated without proof.
The generalization from the original real vector spaces to present complex ones is valid, and completely straightforward.
Note that the interpretation of magnitude and the inner product has to be changed accordingly.
\Result
{Lemma}
{
With the assumption that \m {\M {P}} satisfies RIP for \m {\d_S \SB {\M {P}}},
\PF {d-A-B;1,1}
\DispN {
\NC \VNm {\V {d} _{\MC {AB}}} _2
\leq \NC \F {1} {1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2 +\F {\d_{3S}} {\RB {1-\d_{2S}} \R {S}} \VNm {d_{\MC {C}}} _1 \NR
}
}
And
\Result
{Lemma}
{
\PF {d-A-B;1,1}
\DispN {
\NC \VNm {\V {d}} _2^2
\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1} {S} \VNm {\V {d} _{\MC {C}}} _1^2 \NR
}
}

@@

We are going to combine previous lemmata and show the main result.
Now, in view of the result in Section 3.1, \m {s} is free, and we set
\PF {s,1,,}
\DispN {
\NC s
=\NC 1 \NR
}
which is crude, but enough.
Accordingly,
\PF {S;L,nn-hh}
\DispN {
\NC S
=\NC L \R {\log N_H} \NR
}
Just for simplicity, we assume
\PF {d'-S;1,2}
\DispN {
\NC \d_S
\leq \NC \F {1} {2} \NR
}
and
\PF {L;4,}
\DispN {
\NC L
\geq \NC 4 \NR
}

\Result
{Theorem}
{
Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as ()....
Then the bound
\PF {d;4,2}
\DispN {
\NC \VNm {\V {d}} _2
\leq \NC 4 \R {2} \D \R {L \log N_H} \NR
}
holds for probability \m {p}, with
\DispN {
\NC 1 -p
\leq \NC 2 \D 6^L \D \exp \SB {-\F {N_Y^2} {32}} \NR
}
}

By the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {s,1,,} and \Rf {P,P,d},
\PF {P-A-B,P,d}
\DispN {
\NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
\leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
\NC \leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
\NC \leq \NC 4 \R {2 L \log N_H} \NR
}

By \m {\ell_p} norm inequality, by the definition of truncation, by \Rf {d-A-B;1,1}, \PF {d'-S;1,2}, and \PF {P-A-B,P,d} just above,

\PF {d-A;L,d-A}
\DispN {
\NC \VNm {\V {d} _{\MC {A}}} _1
\leq \NC \R {L} \VNm {\V {d} _{\MC {A}}} _2 \NR
\NC \leq \NC \R {L} \VNm {\V {d} _{\MC {AB}}} _2 \NR
\NC \leq \NC 8 \R {2 \log N_H}
+\F {1} {\R{L} \RB {\log N_H} ^{1/4}} \VNm {\V {d} _{\MC {C}}} _1 \NR
}

Next, we want to use \Rf {d-K;d-A,2-g-K} to eliminate \m {\VNm {d _{\MC {A}}} _1} in \Rf {d-A;L,d-A}.
\PF {;8,2,nn-hh}
\DispN {
\NC \leq \NC 8 \R {2 \log N_H}
+\F {1} {\R{L} \RB {\log N_H} ^{1/4}} \RB {\VNm {\V {d} _{\MC {A}}} _1 +2\VNm {\V {g} _{\MC {C}}} _1} \NR
\NC \leq \NC 8 \R {2 \log N_H}
+\F {2} {\R{L} \RB {\log N_H} ^{1/4}} \VNm {\V {g} _{\MC {C}}} _1 \NR
}
And \Rf {g-C;4,p'-2} in Section 3.1 gives
\PF {d-A;8,2}
\DispN {
\NC \VNm {\V {d} _{\MC {A}}} _1
\leq \NC 8 \R {2 \log N_H}
+2\VNm {\V {g} _{\MC {C}}} _1 \NR
\NC \leq \NC \RB {16 \R {2} +\F {4} {\pi^2} \R {1 -\F {2} {\pi}}} \log N_H \NR
}

We are now in a position to bound \m {\VNm {d} _2^2}.
Using Lemma () again, we have
\DispN {
\NC \VNm {\V {d}} _2^2
\leq \NC 32 S \log N_H
+8 \d_{3S} \R {2 \log N_H} 
+\F {\d_{3S}^2} {S} \VNm {\V {d} _{\MC {C}}} _1 \NR
}
Finally, plug in the bound for \m {\VNm {\V {d} _{\MC {C}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d} _{\MC {C}}} _1}.
Again for simplicity, we keep only the first order small terms.
\DispN {
\NC \VNm {\V {d}} _2^2
\leq \NC 32 S \log N_H
+\F {8 \R {2\pi}} {3} \d_{3S} L \R {\F {\log N_H} {N_H}}
+\F {\pi} {9} \F {L} {s^2 N_H} \NR
}
Set \m {\d_S =1} for the worst situation, and we get the desired bound.

### 2019-09-22 paper/4_simulation.tex
Use BibTeX, conform to IEEE citation style

@@

>>>>

We do three series of experiments, which are of size from small to large.
In three experiments, we take respectively \m {L} to be \m {2, 3, 4}, \m {N_Y} to be \m {5, 7, 9}, \m {N_R} to be \m {10, 14, 18}, and \m {N_H} to be \m {20, 28, 36}.

Other parameters are fixed in these experiments; 
The number of grid of quantization of analog precoder is 16
The wavelength of the EM wave that antenna is emitting, \m {\l _{\Rm{ant}} = 1}, is set to be 0.1.
and the antenna spacing \m {d _{\Rm{ant}} =3}.
Note that only their ratio matters.
See chapter 2 for meaning of them.

There are also parameters related to the convex optimization algorithm.
The tolerance of absolute error in the primal-dual algorithm used in CVXPY is set as \m {10^{-4}}, and the tolerance of relative error, as \m {10^{-3}}.
The maximal number of iteration of CVXPY is set to be \m {32}.
On the other hand, the maximal number of iteration of OMP is set to be \m {4 N_H}.

Each data point is repeated for 32 times, and taken average.
We plot the absolute log error
\DispN {
\NC \eta_{\Rm{abs}}
=\NC \RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}, \NR
}
and relative log error.
\DispN {
\NC \eta_{\Rm{rel}}
=\NC \F {\RB {\log_2 {\VNm {\V {h} -\Hat {\V {h}}}_2}} _{\Ss{avg}}}
{\RB {\log_2 {\VNm {\V {h}}_2}} _{\Ss{avg}}} \NR
}
The averaged error values are plotted along with the theoretical expected error of DS, derived in chap.\ 3, namely
\DispN {
\NC \eta_{\Rm{th}}
=\NC \F{5}{2} + \log \RB{L N_H} + \log \log N_H \NR
}

Several threshold values occur in relevant alorithms.
The threshold used in DS program is called \m {\g_{\Rm {DS}}} here, and another threshold of Lasso, called \m {\a}.
Yet another threshold used for the residue norm used in OMP program is called \m {\eta}.
Various several values are tried for them, determined as thus: Take a central value roughly corresponding to the theory, and mutiply or divided the central value by powers of 2, or

Concretely, we set \m {\g_{\Rm {DS}} = 2 \R {\log N_H}}, corresponding to Cand\`es \& Tao (2007)
For comparison, \m {\g_{\Rm {Lasso}} = 2 \R {\log N_H}} too.
For OMP, suggested values in Cai \& Wang (2011) is illuminating.
There, Theorem 7 considered \m {\ell _2}-norm, and Theorem 8, \m {\ell _\infty}-norm.
We make simplification and set respectively \m {\R {3} N_Y} and \m {2 \R {\log N_H}}

@@

\startsubsection [title={On Complexity}]

In general, complexity analysis of convex program is difficult, in that it is not easily ensured how many iteration the program uses.
Specifically, the implementers of CVXPY, Diamond and Boyd \cite [DiB16], alleges that the program is usually converted in to primal-dual problem.

However, if we use Newton method and assume self-concordance, there is an analysis in B \& V.
Such analysis, in our opinion, still gives us an idea about the complexity of the DS program.

It can be shown that DS can be cast into an Second Order Cone Programming (SOCP), and it is clear that self concordance applies to SOCP.

The function being minimized is \m {\underset {x} {\Rm{min}} \VNm {\V {g}}_1}.
Let \m {\V {g} _0} denote the starting value of \m {\V {g}}, and \m {\V {g} ^{\star}} the the point of convergence.
Then the number of iteration of Newton method is bounded by
\DispN {
\NC \F {\VNm {\V {g}} _1 - \VNm {\V {g} ^{\star}}} {\g} + \log_2 \log_2 \F {1} {\e} \NR
}
Here \m {\g} is a parameter related to the Backtracking algorithm, and \m {\e} the tolerance of error.
The details can be found in Boyd \& Vandenberghe (2004).
They cites various numerical experiements, and it turns out almost always that a value of \m {\g} close to 1 gives the best result, so we take \m {\g} as a constant.

Numerically, we see that the complexity of DS is generally very high.
But it also depends on the tolerence of error.
% XXX criticism on DS complexity?
